Multiproxy analysis exploring patterns of diet and disease in dental calculus and skeletal remains from a 19th century Dutch population

### 2023-11-03 analysis/paper/paper.tex
feat: formatting for PCI_Archaeo

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=30mm,left=30mm,heightrounded]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{lineno}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Multiproxy analysis exploring patterns of diet and disease in dental calculus and skeletal remains from a 19th century Dutch population},
  pdfauthor={Bjørn Peare Bartholdy; Jørgen B. Hasselstrøm; Lambert K. Sørensen; Maia Casna; Menno Hoogland; Historisch Genootschap Beemster; Amanda G. Henry},
  pdfkeywords={dental calculus; LC-MS/MS; alkaloids; dental pathology;
sinusitis; caffeine; tobacco},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
%% modified from: https://github.com/quarto-journals/plos/blob/main/_extensions/plos/partials/before-body.tex
\begin{flushleft}
{\LARGE
\textbf\newline{Multiproxy analysis exploring patterns of diet and
disease in dental calculus and skeletal remains from a 19th century
Dutch population}
}
\newline

\vspace{12pt}
% Insert author names, affiliations and corresponding author email

\normalsize{Bjørn Peare
Bartholdy}\textsuperscript{1*}, \normalsize{Jørgen B.
Hasselstrøm}\textsuperscript{2}, \normalsize{Lambert K.
Sørensen}\textsuperscript{2}, \normalsize{Maia
Casna}\textsuperscript{1}, \normalsize{Menno
Hoogland}\textsuperscript{1}, \normalsize{Historisch Genootschap
Beemster}\textsuperscript{3}, \normalsize{Amanda G.
Henry}\textsuperscript{1}
\\
\bigskip
\small{1} \small{Department of Archaeological Sciences, Leiden
University}\\ \small{2} \small{Department of Forensic Medicine, Aarhus
University}\\ \small{3} \small{Historisch Genootschap Beemster}
\newline

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* b.p.bartholdy@arch.leidenuniv.nl

\end{flushleft}

\linenumbers

@@

Keywords:  dental calculus; LC-MS/MS; alkaloids; dental pathology;
sinusitis; caffeine; tobacco 
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, boxrule=0pt, sharp corners, breakable, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{materials}{%
\subsection{Materials}\label{materials}}

@@

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{skeletal-analysis}{%
\subsubsection{Skeletal analysis}\label{skeletal-analysis}}

@@

\hypertarget{paleopathology}{%
\paragraph{Paleopathology}\label{paleopathology}}

@@

\hypertarget{dental-pathology}{%
\paragraph{Dental pathology}\label{dental-pathology}}

@@

\hypertarget{calculus-sampling}{%
\subsubsection{Calculus sampling}\label{calculus-sampling}}

@@

\hypertarget{uhplc-msms}{%
\subsubsection{UHPLC-MS/MS}\label{uhplc-msms}}

@@

\hypertarget{statistical-analysis}{%
\subsubsection{Statistical analysis}\label{statistical-analysis}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

\hypertarget{correlations-between-detected-alkaloids-and-diseases}{%
\subsubsection{Correlations between detected alkaloids and
diseases}\label{correlations-between-detected-alkaloids-and-diseases}}

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

@@

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

@@

\hypertarget{acknowledgements}{%
\subsection*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{subsection}{Acknowledgements}

@@

@@

\hypertarget{data-availability-statement}{%
\subsection*{Data Availability
Statement}\label{data-availability-statement}}
\addcontentsline{toc}{subsection}{Data Availability Statement}

@@

\hypertarget{conflict-of-interest-disclosure}{%
\subsection*{Conflict of interest
disclosure}\label{conflict-of-interest-disclosure}}
\addcontentsline{toc}{subsection}{Conflict of interest disclosure}

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=10mm,bottom=10mm,left=30mm,heightrounded]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{fancyhdr, graphicx}
\usepackage[hidelinks]{hyperref}

\fancyhead{\vspace{70pt}}
\renewcommand{\headrulewidth}{1.8pt}

\makeatletter
\def\@maketitle{%
  \newpage
  \hfill\href{https://doi.org/10.24072/pci.archaeo.100389}{\includegraphics[width=3.5cm]{badge_PCI_Archaeology.png}}\hfill
  \null
 \begin{center}
{\LARGE
\textbf\newline{\@title}
}
%\newline

\end{center}
  \par}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Multiproxy analysis exploring patterns of diet and disease in dental calculus and skeletal remains from a 19th century Dutch population},
  pdfauthor={Bjørn Peare Bartholdy; Jørgen B. Hasselstrøm; Lambert K. Sørensen; Maia Casna; Menno Hoogland; Historisch Genootschap Beemster; Amanda G. Henry},
  pdfkeywords={dental calculus; LC-MS/MS; alkaloids; dental pathology;
sinusitis; caffeine; tobacco},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
%% modified from: https://github.com/quarto-journals/plos/blob/main/_extensions/plos/partials/before-body.tex

\maketitle

\begin{center}

\thispagestyle{fancy}

% Insert author names, affiliations and corresponding author email

\normalsize{Bjørn Peare
Bartholdy}\textsuperscript{1*}, \normalsize{Jørgen B.
Hasselstrøm}\textsuperscript{2}, \normalsize{Lambert K.
Sørensen}\textsuperscript{2}, \normalsize{Maia
Casna}\textsuperscript{1}, \normalsize{Menno
Hoogland}\textsuperscript{1}, \normalsize{Historisch Genootschap
Beemster}\textsuperscript{3}, \normalsize{Amanda G.
Henry}\textsuperscript{1}\vspace{12pt}

\rule{\textwidth}{1.8pt}\vspace{8pt}

\end{center}

\textsuperscript{\footnotesize{1}}\textit{\small{Department of
Archaeological Sciences, Leiden
University}}\\ \textsuperscript{\footnotesize{2}}\textit{\small{Department
of Forensic Medicine, Aarhus
University}}\\ \textsuperscript{\footnotesize{3}}\textit{\small{Historisch
Genootschap Beemster}}

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* \small{b.p.bartholdy@arch.leidenuniv.nl}

\vspace{12pt}

@@

\small \textbf{Keywords:}  dental calculus; LC-MS/MS; alkaloids; dental
pathology; sinusitis; caffeine; tobacco   \\

\vfill

\newgeometry{top=30mm,left=30mm}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{materials}{%
\section{Materials}\label{materials}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{skeletal-analysis}{%
\subsection{Skeletal analysis}\label{skeletal-analysis}}

@@

\hypertarget{paleopathology}{%
\subsubsection{Paleopathology}\label{paleopathology}}

@@

\hypertarget{dental-pathology}{%
\subsubsection{Dental pathology}\label{dental-pathology}}

@@

\hypertarget{calculus-sampling}{%
\subsection{Calculus sampling}\label{calculus-sampling}}

@@

\hypertarget{uhplc-msms}{%
\subsection{UHPLC-MS/MS}\label{uhplc-msms}}

@@

\hypertarget{statistical-analysis}{%
\subsection{Statistical analysis}\label{statistical-analysis}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{correlations-between-detected-alkaloids-and-diseases}{%
\subsection{Correlations between detected alkaloids and
diseases}\label{correlations-between-detected-alkaloids-and-diseases}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

@@

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

@@

\hypertarget{funding}{%
\section*{Funding}\label{funding}}
\addcontentsline{toc}{section}{Funding}

@@

\hypertarget{conflict-of-interest-disclosure}{%
\section*{Conflict of interest
disclosure}\label{conflict-of-interest-disclosure}}
\addcontentsline{toc}{section}{Conflict of interest disclosure}

\hypertarget{data-availability-statement}{%
\section*{Data Availability
Statement}\label{data-availability-statement}}
\addcontentsline{toc}{section}{Data Availability Statement}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}
